Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-08-01 paper/paper.tex
tasks

>>>>

Since we expect/hope that the optimized network extends this range of possible frequencies,
we choose the frequencies for the optimiztion tasks from the slighly larger interval 
$[0.6e-2, 4]$ such that their logarithms are uniformly spaced. This allows for good resolution 
for both high and low frequencies.
